---
title: "Commands"
author: "Mohammad Mahdi Bagheri Asl"
date: "2023-05-18"
output: html_document
---
#Coursera - R-Specializatoin 

##list installed packages
```{r}
installed.packages()
library()
```

##update installed packages
```{r}
old.packages()
update.packages()
install.packages("package-name")
```

##detach and remove installed packages
```{r}
detach("package:ggplot2", unload = T)
remove.packages()
```

##list loadde packages
```{r}
sessionInfo()
search()
```

##help and vignettes
```{r}
help(package = "package-name")
browseVignettes("package-name")
```

## Create a Git token and push it in Rstudio
```{r}
install.packages("usethis")
library(usethis)
use_git_config(user.name = "", user.email = "")
create_github_token()
install.packages("gitcreds")
library(gitcreds)
gitcreds_set()
```

##push a existing project to GIT (terminal code)
cd /repo_directory
git init
git add .
git commit -m "initial commit"

**create a git repo**
git remote add origin git@github.com:git_username/repo_name.git
git branch -M main
git push -u origin main

##RMarkdown
```{r}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```


